Quantifying the rock-paper-scissors effect

### 2024-08-15 inst/rock_paper_scissors_monster.Rmd
dirichlet3()

```{r,label=defineh3seven}
H3seven <- function(lambda){
  H3 <- hyper3()
  for(i in 1:6){
     jj <- 1  # diagonal players do not have lambda-advantage
     names(jj) <- tt[i]
     H3[jj] %<>% inc(hw[i,i])

     jj <- lambda
     names(jj) <- tt[i+1]
     H3[jj] %<>% inc(hw[i,i+1])

     jj <- c(1,lambda)
     names(jj) <- c(tt[i],tt[i+1])
     H3[jj] %<>% dec(hw[i,i] + hw[i,i+1])
  }  # i loop closes

  ## Now do final one:
  jj <- 1
  names(jj) <- tt[7]
  H3[jj] %<>% inc(hw[7,7])

  jj <- lambda
  names(jj) <- tt[1]
  H3[jj] %<>% inc(hw[7,1])

  jj <- c(1,lambda)
  names(jj) <- c(tt[7],tt[1])
  H3[jj] %<>% dec(hw[7,7] + hw[7,1])

  return(H3)
}  # function H3seven() defn closes
```

Now we can execute it:

```{r,label=executeh3seven}
H3 <- H3seven(lambda=1.66)
H3
```

```{r,label=defineproflikeh3}
profl <- function(lambda){
  H <- H3seven(lambda)
  return(loglik(maxp(H),H))
}
```

>>>>

```{r,label=defineh3seven}
H3seven <- function(lambda){
    out <- hyper3()
    for(i in 1:6){
        out %<>% inc(dirichlet3(powers=hw[i,i:(i+1)],lambda=c(1,lambda)))
    }
    out %<>% inc(dirichlet3(powers=hw[7,c(7,1)],lambda=c(1,lambda)))
    return(out)
}
H3seven(lambda=1.66)
```

```{r,label=defineproflikeh3seven}
profl <- function(lambda){
  H <- H3seven(lambda)
  return(loglik(maxp(H),H))
}
```
